The role of cognateness in non-native spoken word recognition

### 2021-12-20 manuscript/manuscript.Rmd
Reorganise repo

# set custom ggplot2 theme
theme_set(
  theme(
    title = element_text(size = 8, face = "bold"),

    legend.background = element_rect(fill = NA, colour = NA),
    legend.key = element_rect(fill = "white", colour = NA),
    legend.justification = "right",
    legend.direction = "horizontal",

    axis.line = element_line(colour = "black", size = 0.5),
    axis.ticks = element_line(colour = "black", size = 0.5),
    axis.text.x = element_text(colour = "black"),
    axis.text.y = element_text(colour = "black"),

    plot.caption.position = "plot",
    plot.title = element_text(hjust = 0.5),

    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white", colour = NA)
  )
)

@@

include_graphics(here("Figures", "design.png"))

@@

tb_stimuli <- stimuli %>% 
  select(group, word1, frequency, frequency_zipf, pthn, lv) %>% 
  group_by(group) %>% 
  summarise_at(
    vars(frequency:lv), 
    list(
      mean = ~mean(., na.rm = TRUE),  
      sd = ~sd(., na.rm = TRUE)
    )
  ) %>%
  gt(rowname_col = "group") %>% 
  tab_header(
    title = md("Table 1"),
    subtitle = md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")
  ) %>% 
  tab_source_note(
    md("*Note*. Mean and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")
  ) %>% 
  fmt_number(frequency_mean:pthn_sd) %>%
  fmt_percent(matches("lv")) %>% 
  tab_spanner(md("**Freq. (million)**"), c("frequency_mean", "frequency_sd")) %>% 
  tab_spanner(md("**Freq. (Zipf)**"), matches("frequency_zipf")) %>% 
  tab_spanner(md("***PTHN***"), matches("pthn")) %>% 
  tab_spanner(md("**Levenshtein**"), matches("lv")) %>% 
  cols_label(
    frequency_mean = md("Mean"),
    frequency_sd = md("*SD*"),
    frequency_zipf_mean = md("Mean"),
    frequency_zipf_sd = md("*SD*"),
    pthn_mean = md("Mean"),
    pthn_sd = md("*SD*"),
    lv_mean = md("Mean"),
    lv_sd = md("*SD*")
  ) %>% 
  summary_rows(
    columns = c(matches("mean"), -matches("lv")),
    fns = list(
      Mean = "mean",
      SD = "sd"
    )
  ) %>% 
  summary_rows(
    columns = matches("lv"),
    fns = list(
      Mean = "mean",
      SD = "sd"
    ), formatter = fmt_percent
  ) %>% 
  tab_style(
    style = cell_text(align = "left", weight = "bold", size = "medium"),
    locations = cells_title(groups = "title")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium", style = "italic"),
    locations = cells_title(groups = "subtitle")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_source_notes()
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_stub_grand_summary()
  ) %>% 
  tab_style(
    style = cell_borders(sides = c("left", "right"), color = "white"),
    locations = list(
      cells_body(), cells_row_groups(), cells_column_spanners(), 
      cells_stub(), cells_stub_grand_summary(), cells_source_notes(),
      cells_column_labels(), cells_stubhead()
    )
  ) %>% 
  tab_style(
    style = list(cell_text(align = "left", size = "medium"), cell_borders(sides = "all", color = "white")),
    locations = cells_stub()
  ) %>% 
  tab_style(
    style = cell_text(align = "center", size = "medium", weight = "normal", style = "normal"),
    locations = list(cells_column_spanners(), cells_column_labels())
  ) %>% 
  tab_style(
    style = cell_borders(sides = "all", color = "white"),
    locations = cells_body(columns = 1:9)
  ) %>% 
  tab_style(
    style = cell_borders(sides = "top", color = "white"),
    locations = cells_body(columns = 1:9)
  ) %>% 
  gtsave(here("Figures", "stimuli.png"))

include_graphics(here("Figures", "stimuli.png"), auto_pdf = FALSE)

@@

include_graphics(here("Figures", "loos.png"))

@@

```{r posteriorfix, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Estimated posterior distributions of coefficients in Model 4. A\\) Population-level effects. Distributions indicate the estimated posterior likelihood density of regression coefficients of fixed effects. Credible intervals (*CrI*), represented with increasingly lighter segmentents in the distribution indicate the range of values that contain the true value with 95\\%, 80\\%, and 50\\% probability. Black dots represent the mean of each distribution. B\\) Participant\\-level coefficient variability. The model estimated participant\\-level coefficients to account for the dependency between responses from the same participant. Distributions in this panel indicate the estimated variability across coefficients from different participants, expressed as standard deviations (*SD*). C\\) Correlation between participant\\-level effects. The model allowed participant-level coefficients to co\\-vary. This panel represents the Pearson correlations between each pair of coefficients, expressed as the mean of the posterior distribution of each  estimated correlation.", fig.height=7, fig.width=6.5}

@@

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf" = "Frequency\n[+1 SD]",
  "pthn:lv" = "PTHN \u00d7 Levenshtein", 
  "lv:group1" = "Levenshtein \u00d7 Group 1",
  "lv:group2" = "Levenshtein \u00d7 Group 2",
  "lv" = "Levenshtein\n[+1 SD]",
  "pthn" = "PTHN\n[+1 SD]",
  "group1" =  "Group 1\n[ENG-* vs. SPA-CAT]",
  "group2" = "Group 2\n[ENG-CAT vs. ENG-SPA]"
)

@@

```{r bayesfactors}
h_frequency <- abs(hypothesis(model_fits$fit_6, hypothesis = "frequency_zipf = 0")$hypothesis$Evid.Ratio)
h_pthn <- abs(hypothesis(model_fits$fit_6, hypothesis = "pthn = 0")$hypothesis$Evid.Ratio)
h_lv <- abs(hypothesis(model_fits$fit_6, hypothesis = "lv = 0")$hypothesis$Evid.Ratio)
h_pthn_lv <- abs(hypothesis(model_fits$fit_6, hypothesis = "pthn:lv = 0")$hypothesis$Evid.Ratio)
h_group1 <- abs(hypothesis(model_fits$fit_6, hypothesis = "group1 = 0")$hypothesis$Evid.Ratio)
h_group2 <- abs(hypothesis(model_fits$fit_6, hypothesis = "group1 = 0")$hypothesis$Evid.Ratio)
h_lv_group1 <- abs(hypothesis(model_fits$fit_6, hypothesis = "lv:group1 = 0")$hypothesis$Evid.Ratio)
h_lv_group2 <- abs(hypothesis(model_fits$fit_6, hypothesis = "lv:group2 = 0")$hypothesis$Evid.Ratio)

@@

h_cor_intercept_frequency <- hypothesis(model_fits$fit_6, "participant__Intercept__frequency_zipf = 0", class = "cor")$hypothesis$Evid.Ratio
h_cor_frequency_zipf_lv_group1 <- hypothesis(model_fits$fit_6, "participant__frequency_zipf__lv:group1 = 0", class = "cor")$hypothesis$Evid.Ratio
h_cor_intercept_pthn <- hypothesis(model_fits$fit_6, "participant__Intercept__pthn = 0", class = "cor")$hypothesis$Evid.Ratio
```

@@

Spanish natives translating Catalan words were `r percent(coefs$group1["estimate"], accuracy = 0.01)` more accurate than English natives translating Spanish and Catalan words (95% *CrI* = [`r percent(coefs$group1["q2_5"], accuracy = 0.01)`, `r percent(coefs$group1["q97_5"], accuracy = 0.01)`], $BF_{\beta \neq 0}$ = `r printnum(h_group1)`). This difference increased in `r percent(coefs$lv_group1["estimate"], accuracy = 0.01)` for every one *SD* increment in Levenshtein similarity (95% *CrI* = [`r percent(coefs$lv_group1["q2_5"], accuracy = 0.01)`, `r percent(coefs$lv_group1["q97_5"], accuracy = 0.01)`], $BF_{\beta \neq 0}$ = `r printnum(h_lv_group1)`). English natives translating Catalan words were `r percent(abs(coefs$group2["estimate"]), accuracy = 0.01)` more accurate than those translating Spanish words (95% *CrI* = [`r percent(coefs$group2["q2_5"], accuracy = 0.01)`, `r percent(coefs$group2["q97_5"], accuracy = 0.01)`], $BF_{\beta \neq 0}$ = `r printnum(h_group2)`). For every one *SD* increment in Levenshtein similarity, the effect increased in `r percent(abs(coefs$lv_group2["estimate"]), accuracy = 0.01)` (95% *CrI* = [`r percent(coefs$lv_group2["q2_5"], accuracy = 0.01)`, `r percent(coefs$lv_group2["q97_5"], accuracy = 0.01)`], $BF_{\beta \neq 0}$ = `r printnum(h_lv_group1)`).

@@

The conditional intra-class correlation (*ICC*) for items was `r percent(icc_conditional, accuracy = 0.01)`, indicating that responses from different participants to the same item were, on average, more similar to each other than responses to other items [@gelman2006data]. Item-level intercepts showed remarkable variability (*SD* = `r percent(sds$sd_word_intercept$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_word_Intercept$.lower, accuracy = 0.01)`, `r percent(sds$sd_word_Intercept$.upper, accuracy = 0.01)`]), indicating that participants' accuracy differed substantially across words: some words were correctly translated nearly always (e.g., Spanish *tomate*-*tomato*, /tomate/-/təmɑːtoʊ/, `r percent(word_example$tomate$estimate, accuracy = 0.01)`, 95% CrI = [`r percent(word_example$tomate$q2_5, accuracy = 0.01)`, `r percent(word_example$tomate$q97_5, accuracy = 0.01)`]), while others were almost never translated correctly (e.g., Catalan *colom*-*pigeon*, /kulom/-/pɪdʒɪn/, `r percent(word_example$colom$estimate, accuracy = 0.01)`, 95% CrI = [`r percent(word_example$colom$q2_5, accuracy = 0.01)`, `r percent(word_example$colom$q97_5, accuracy = 0.01)`]). Participant-level intercepts also showed high variability (*SD* = `r percent(sds$sd_participant_intercept$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_participant_intercept$.lower, accuracy = 0.01)`, `r percent(sds$sd_participant_intercept$.upper, accuracy = 0.01)`]), suggesting that average translation accuracy also varied significantly across participants. Finally, participant-level estimated slopes showed less variability: *SD* of $Frequency$, $PTHN$, $Levenshtein$, $PTHN \times Levenshtein$, and $Levenshtein \times Group 2$ ranged between `r percent(participant_ranef_range[1], accuracy = 0.01)`, and `r percent(participant_ranef_range[2], accuracy = 0.01)`. The participant-level estimated slopes of the $Leveshtein \times Group 1$ interaction are an exception, though (*SD* = `r percent(sds$sd_participant_lv_group1$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_participant_lv_group1$.lower, accuracy = 0.01)`, `r percent(sds$sd_participant_lv_group1$.upper, accuracy = 0.01)`]). This indicates that the impact of phonological similarity ($Levenshtein$) on the difference in accuracy between English and Spanish natives differed substantially across participants.

>>>>

# set custom ggplot2 theme
theme_set(theme_custom()) # in utlis.R

@@

include_graphics(here("img", "design.png"))

@@

tb_stimuli <- stimuli %>% 
  select(group, word1, frequency, frequency_zipf, pthn, lv) %>% 
  group_by(group) %>% 
  summarise_at(
    vars(frequency:lv), 
    list(
      mean = ~mean(., na.rm = TRUE),  
      sd = ~sd(., na.rm = TRUE)
    )
  ) %>%
  gt(rowname_col = "group") %>% 
  tab_header(
    title = md("Table 1"),
    subtitle = md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")
  ) %>% 
  tab_source_note(
    md("*Note*. Mean and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")
  ) %>% 
  fmt_number(frequency_mean:pthn_sd) %>%
  fmt_percent(matches("lv")) %>% 
  tab_spanner(md("**Freq. (million)**"), c("frequency_mean", "frequency_sd")) %>% 
  tab_spanner(md("**Freq. (Zipf)**"), matches("frequency_zipf")) %>% 
  tab_spanner(md("***PTHN***"), matches("pthn")) %>% 
  tab_spanner(md("**Levenshtein**"), matches("lv")) %>% 
  cols_label(
    frequency_mean = md("Mean"),
    frequency_sd = md("*SD*"),
    frequency_zipf_mean = md("Mean"),
    frequency_zipf_sd = md("*SD*"),
    pthn_mean = md("Mean"),
    pthn_sd = md("*SD*"),
    lv_mean = md("Mean"),
    lv_sd = md("*SD*")
  ) %>% 
  summary_rows(
    columns = c(matches("mean"), -matches("lv")),
    fns = list(
      Mean = "mean",
      SD = "sd"
    )
  ) %>% 
  summary_rows(
    columns = matches("lv"),
    fns = list(
      Mean = "mean",
      SD = "sd"
    ), formatter = fmt_percent
  ) %>% 
  tab_style(
    style = cell_text(align = "left", weight = "bold", size = "medium"),
    locations = cells_title(groups = "title")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium", style = "italic"),
    locations = cells_title(groups = "subtitle")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_source_notes()
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_stub_grand_summary()
  ) %>% 
  tab_style(
    style = cell_borders(sides = c("left", "right"), color = "white"),
    locations = list(
      cells_body(), cells_row_groups(), cells_column_spanners(), 
      cells_stub(), cells_stub_grand_summary(), cells_source_notes(),
      cells_column_labels(), cells_stubhead()
    )
  ) %>% 
  tab_style(
    style = list(cell_text(align = "left", size = "medium"), cell_borders(sides = "all", color = "white")),
    locations = cells_stub()
  ) %>% 
  tab_style(
    style = cell_text(align = "center", size = "medium", weight = "normal", style = "normal"),
    locations = list(cells_column_spanners(), cells_column_labels())
  ) %>% 
  tab_style(
    style = cell_borders(sides = "all", color = "white"),
    locations = cells_body(columns = 1:9)
  ) %>% 
  tab_style(
    style = cell_borders(sides = "top", color = "white"),
    locations = cells_body(columns = 1:9)
  ) %>% 
  gtsave(here("img", "stimuli.png"))

include_graphics(here("img", "stimuli.png"), auto_pdf = FALSE)

@@

include_graphics(here("img", "loos.png"))

@@

```{r posteriorfix, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Estimated posterior distributions of coefficients in Model 6. A\\) Population-level effects. Distributions indicate the estimated posterior likelihood density of regression coefficients of fixed effects. Credible intervals (*CrI*), represented with increasingly lighter segmentents in the distribution indicate the range of values that contain the true value with 95\\%, 80\\%, and 50\\% probability. Black dots represent the mean of each distribution. B\\) Participant\\-level coefficient variability. The model estimated participant\\-level coefficients to account for the dependency between responses from the same participant. Distributions in this panel indicate the estimated variability across coefficients from different participants, expressed as standard deviations (*SD*). C\\) Correlation between participant\\-level effects. The model allowed participant-level coefficients to co\\-vary. This panel represents the Pearson correlations between each pair of coefficients, expressed as the mean of the posterior distribution of each  estimated correlation.", fig.height=7, fig.width=6.5}

@@

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf" = "Frequency\n[+1 SD]",
  "pthn:lv" = "PTHN \u00d7 Levenshtein", 
  "lv:groupENGvs.SPA" = "Levenshtein \u00d7 Group 1",
  "lv:groupENGMCATvs.ENGMSPA" = "Levenshtein \u00d7 Group 2",
  "lv" = "Levenshtein\n[+1 SD]",
  "pthn" = "PTHN\n[+1 SD]",
  "groupENGvs.SPA" =  "Group 1\n[ENG-* vs. SPA-CAT]",
  "groupENGMCATvs.ENGMSPA" = "Group 2\n[ENG-CAT vs. ENG-SPA]"
)

@@

```{r bayesfactors}
h_frequency <- abs(hypothesis(model_fits$fit_6, hypothesis = "frequency_zipf = 0")$hypothesis$Evid.Ratio)
h_pthn <- abs(hypothesis(model_fits$fit_6, hypothesis = "pthn = 0")$hypothesis$Evid.Ratio)
h_lv <- abs(hypothesis(model_fits$fit_6, hypothesis = "lv = 0")$hypothesis$Evid.Ratio)
h_pthn_lv <- abs(hypothesis(model_fits$fit_6, hypothesis = "pthn:lv = 0")$hypothesis$Evid.Ratio)
h_group1 <- abs(hypothesis(model_fits$fit_6, hypothesis = "groupENGvs.SPA = 0")$hypothesis$Evid.Ratio)
h_group2 <- abs(hypothesis(model_fits$fit_6, hypothesis = "groupENGMCATvs.ENGMSPA = 0")$hypothesis$Evid.Ratio)
h_lv_group1 <- abs(hypothesis(model_fits$fit_6, hypothesis = "lv:groupENGvs.SPA = 0")$hypothesis$Evid.Ratio)
h_lv_group2 <- abs(hypothesis(model_fits$fit_6, hypothesis = "lv:groupENGMCATvs.ENGMSPA = 0")$hypothesis$Evid.Ratio)

@@

h_cor_intercept_frequency <- hypothesis(
  model_fits$fit_6, 
  "participant__Intercept__frequency_zipf = 0", 
  class = "cor"
  )$hypothesis$Evid.Ratio

h_cor_frequency_zipf_lv_group1 <- hypothesis(
  model_fits$fit_6, 
  "participant__frequency_zipf__lv:groupENGMCATvs.ENGMSPA  = 0", 
  class = "cor"
  )$hypothesis$Evid.Ratio

h_cor_intercept_pthn <- hypothesis(
  model_fits$fit_6,
  "participant__Intercept__pthn = 0", 
  class = "cor"
  )$hypothesis$Evid.Ratio
```

@@

Spanish natives translating Catalan words were `r percent(coefs$group_en_gvs_spa["estimate"], accuracy = 0.01)` more accurate than English natives translating Spanish and Catalan words (95% *CrI* = [`r percent(coefs$group_en_gvs_spa["q2_5"], accuracy = 0.01)`, `r percent(coefs$group_en_gvs_spa["q97_5"], accuracy = 0.01)`], $BF_{\beta \neq 0}$ = `r printnum(h_group1)`). This difference increased in `r percent(coefs$lv_group_en_gvs_spa["estimate"], accuracy = 0.01)` for every one *SD* increment in Levenshtein similarity (95% *CrI* = [`r percent(coefs$lv_group_en_gvs_spa["q2_5"], accuracy = 0.01)`, `r percent(coefs$lv_group_en_gvs_spa["q97_5"], accuracy = 0.01)`], $BF_{\beta \neq 0}$ = `r printnum(h_lv_group1)`). English natives translating Catalan words were `r percent(abs(coefs$group_engmca_tvs_engmspa["estimate"]), accuracy = 0.01)` more accurate than those translating Spanish words (95% *CrI* = [`r percent(coefs$group_engmca_tvs_engmspa["q2_5"], accuracy = 0.01)`, `r percent(coefs$group_engmca_tvs_engmspa["q97_5"], accuracy = 0.01)`], $BF_{\beta \neq 0}$ = `r printnum(h_group2)`). For every one *SD* increment in Levenshtein similarity, the effect increased in `r percent(abs(coefs$lv_group_engmca_tvs_engmspa["estimate"]), accuracy = 0.01)` (95% *CrI* = [`r percent(coefs$lv_group_engmca_tvs_engmspa["q2_5"], accuracy = 0.01)`, `r percent(coefs$lv_group_engmca_tvs_engmspa["q97_5"], accuracy = 0.01)`], $BF_{\beta \neq 0}$ = `r printnum(h_lv_group1)`).

@@

The conditional intra-class correlation (*ICC*) for items was `r percent(icc_conditional, accuracy = 0.01)`, indicating that responses from different participants to the same item were, on average, more similar to each other than responses to other items [@gelman2006data]. Item-level intercepts showed remarkable variability (*SD* = `r percent(sds$sd_word_intercept$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_word_Intercept$.lower, accuracy = 0.01)`, `r percent(sds$sd_word_Intercept$.upper, accuracy = 0.01)`]), indicating that participants' accuracy differed substantially across words: some words were correctly translated nearly always (e.g., Spanish *tomate*-*tomato*, /tomate/-/təmɑːtoʊ/, `r percent(word_example$tomate$estimate, accuracy = 0.01)`, 95% CrI = [`r percent(word_example$tomate$q2_5, accuracy = 0.01)`, `r percent(word_example$tomate$q97_5, accuracy = 0.01)`]), while others were almost never translated correctly (e.g., Catalan *colom*-*pigeon*, /kulom/-/pɪdʒɪn/, `r percent(word_example$colom$estimate, accuracy = 0.01)`, 95% CrI = [`r percent(word_example$colom$q2_5, accuracy = 0.01)`, `r percent(word_example$colom$q97_5, accuracy = 0.01)`]). Participant-level intercepts also showed high variability (*SD* = `r percent(sds$sd_participant_intercept$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_participant_intercept$.lower, accuracy = 0.01)`, `r percent(sds$sd_participant_intercept$.upper, accuracy = 0.01)`]), suggesting that average translation accuracy also varied significantly across participants. Finally, participant-level estimated slopes showed less variability: *SD* of $Frequency$, $PTHN$, $Levenshtein$, $PTHN \times Levenshtein$, and $Levenshtein \times Group 2$ ranged between `r percent(participant_ranef_range[1], accuracy = 0.01)`, and `r percent(participant_ranef_range[2], accuracy = 0.01)`. The participant-level estimated slopes of the $Leveshtein \times Group 1$ interaction are an exception, though (*SD* = `r percent(sds$sd_participant_lv_group_en_gvs_spa$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_participant_lv_group_en_gvs_spa$.lower, accuracy = 0.01)`, `r percent(sds$sd_participant_lv_group_en_gvs_spa$.upper, accuracy = 0.01)`]). This indicates that the impact of phonological similarity ($Levenshtein$) on the difference in accuracy between English and Spanish natives differed substantially across participants.

### 2021-12-20 manuscript/manuscript_appendix.Rmd
Reorganise repo

bayesplot_theme_set(
  new = theme_custom() + 
    theme(
      axis.text.x = element_text(size = 8), 
      axis.text.y = element_text(size = 8),
      strip.text = element_text(size = 10),
      legend.key = element_rect(colour = NA, fill = "white")
    )
)

@@

```{r appendix-model-code, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
model_fits$fit_3$model
color_scheme_set(c("#1A85FF", "#9ccaff", "#1A85FF",  "#1A85FF", "#1A85FF", "#1A85FF"))

@@

```{r appendix-mcmc-diagnostics, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
posterior_cp <- as.array(model_fits$fit_3)

plot_pairs <- mcmc_pairs(
  posterior_cp, pars = c("b_Intercept", "b_frequency_zipf", "b_pthn", "b_lv", "b_pthn:lv"),
  off_diag_args = list(size = 0.75),
  alpha = 1, size = 0
)

@@

```{r appendix-trace-plot}
mcmc_trace(model_fits$fit_3, pars = c("b_Intercept", "b_frequency_zipf", "b_pthn", "b_lv", "b_pthn:lv"), n_warmup = 0) +
  annotate(geom = "rect", xmin = -Inf, xmax = 500, ymin = -Inf, ymax = Inf, alpha = 0.5, fill = "grey")

@@

mcmc_rhat(rhats) + 
  mcmc_neff(ratios) +
  plot_layout(guides = "keep", ncol = 1) &
  theme(
    legend.position = "right"
  )

>>>>

suppressWarnings({
  bayesplot_theme_set(
    new = theme_custom() + 
      theme(
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8),
        strip.text = element_text(size = 10),
        legend.key = element_rect(colour = NA, fill = "white")
      )
  )
})

color_scheme_set("brightblue")
pars <- c("b_Intercept", "b_frequency_zipf", "b_pthn", "b_lv", "b_pthn:lv")

@@

```{r appendix-code, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
model_fits$fit_3$model
```

@@

```{r appendix-mcmc, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
posterior_cp <- as.array(model_fits$fit_3)
np_cp <- nuts_params(model_fits$fit_3)

plot_pairs <- mcmc_pairs(
  posterior_cp, pars = pars,
  off_diag_args = list(size = 0.75)
)

@@

```{r appendix-trace, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
(mcmc_trace(model_fits$fit_3, pars) + legend_none()) /
  mcmc_rank_overlay(model_fits$fit_3, pars = pars) +
  plot_layout(guides = "collect") &
  theme(
    legend.position = "top"
  )
```

@@

mcmc_rhat_hist(rhats, binwidth = 0.00025, color = "white") + 
  mcmc_neff_hist(ratios, binwidth = 0.1) +
  plot_layout(guides = "keep", ncol = 1) &
  theme(
    legend.position = "right"
  )
```
